LCS Tool: A Computational Platform for Lagrangian Coherent Structures

### 2014-11-07 main.tex
Change LCS Tool download URL from GitHub to RunMyCode

\begin{sloppypar}
Here we present an algorithmic introduction to geodesic LCS detection.
% FIXME JCompSci editor: Replace GitHub link with http://runmycode.org/
% FIXME Reviewer #3, comment #4: Add documentation within the github repository to show some reference to the APIs and how users may start to run a his/her own application.
% FIXME Reviewer #4: Please make sure the code is downloadable once the paper is published
We then review the implementation of this approach in a computational engine called LCS Tool\footnote{LCS Tool is available at: http://github.com/jeixav/LCS-Tool}. This engine is a library of MATLAB functions that extract LCSs from two-dimensional unsteady flows. The examples we present form demonstration scripts distributed with LCS Tool.
\end{sloppypar}

>>>>

\begin{sloppypar}
Here we present an algorithmic introduction to geodesic LCS detection.
% FIXME Reviewer #3, comment #4: Add documentation within the github repository to show some reference to the APIs and how users may start to run a his/her own application.
% FIXME Reviewer #4: Please make sure the code is downloadable once the paper is published
We then review the implementation of this approach in a computational engine called LCS Tool\footnote{LCS Tool is available at: \url{http://www.runmycode.org/companion/view/908}}.
This engine is a library of MATLAB functions that extract LCSs from two-dimensional unsteady flows. The examples we present form demonstration scripts distributed with LCS Tool.
\end{sloppypar}
